---
title: "CLT_WUP"
author: "Wayne Jarvis"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")

my1000 <- sample(Homers_data , size = 1000, replace=T)

```

```{r}

library(ggplot2)
sampleNumber = sample(1:10000, size = 1000)
library(dplyr)
my1000 <- Homers_data[sampleNumber, ]
names(my1000)
# Basic density
p <- ggplot(my1000, aes(x=kkardashtemp,col=sex)) + 
  geom_density()
p
# Add mean line
p+ geom_vline(aes(xintercept=mean(kkardashtemp)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$kkardashtemp),' sd = ',sd(my1000$kkardashtemp)))
```

```{r}
numb=2
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k2 = x.avg

p <- ggplot(my1000, aes(x=k2)) + 
  geom_density() 
p

# Add mean line
  geom_vline(aes(xintercept=mean(k2)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$k2),' sd = ',sd(my1000$k2)))

```

```{r}
numb = 4
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k4 = x.avg


p <- ggplot(my1000, aes(x=k4),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k4)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 4") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k4),' sd = ',sd(my1000$k4)))

```

```{r}
numb=9
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k9 = x.avg

p <- ggplot(my1000, aes(x=k9)) + 
  geom_density() 
p

# Add mean line
  geom_vline(aes(xintercept=mean(k9)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$k9),' sd = ',sd(my1000$k9)))

```

I analyzed our sample size of 9. According to the Central Limits Theorem, the graph shows that the mean gets closer to 50 if rounded up, while standard deviation is decreasing. This is because it's expected to decrease when the sample standard deviation is 42.0198675541614. When increasing the sample size, we divide the sample standard deviation by square root of 9. This results in 14.0066225 which is similar to the sample size of 14.

```{r}
numb=16
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k16 = x.avg

p <- ggplot(my1000, aes(x=k16)) + 
  geom_density() 
p

# Add mean line
  geom_vline(aes(xintercept=mean(k16)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$k16),' sd = ',sd(my1000$k16)))

```

This graph has a sample size of 16. According to the CLT, standard deviation is expected to decrease due to the sample standard deviation of 42.0198675541614. Dividing this number gives us 10.5049669, which is closer to the result I originally found. Because of this, the graph is becoming symmetrical.

```{r}
numb=25
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k25 = x.avg

p <- ggplot(my1000, aes(x=k25)) + 
  geom_density() 
p

# Add mean line
  geom_vline(aes(xintercept=mean(k25)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$k25),' sd = ',sd(my1000$k25)))

```

This graph has a sample size of 25. The CLT tells us if the mean is rounded up, the standard deviation will go down. The standard deviation is 42.0198675541614. Dividing this by 25 gives us 8.40397351, which is closer to the original result. This rounds down to 8.4, which gives us a symmetrical graph.

```{r}
numb=36
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k36 = x.avg

p <- ggplot(my1000, aes(x=k36)) + 
  geom_density() 
p

# Add mean line
  geom_vline(aes(xintercept=mean(k36)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$k36),' sd = ',sd(my1000$k36)))

```

This graph has a sample size of 36. According to the CLT, as the mean rises, the standard deviation lowers. The sample standard deviation in this case is 42.0198675541614. After dividing this by 36, we get 7.0033126. This number tells us that the result is similar to the one I got, which is rounded to 7.0. This tells us that the graph is symmetrical.
