---
title: "CLT_WUP"
author: "Wayne Jarvis"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

kkardashtemp  see code below

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")

my1000 <- sample(Homers_data , size = 1000, replace=T)

```

```{r}

library(ggplot2)
sampleNumber = sample(1:10000, size = 1000)
library(dplyr)
my1000 <- Homers_data[sampleNumber, ]
names(my1000)
# Basic density
p <- ggplot(my1000, aes(x=kkardashtemp,col=sex)) + 
  geom_density()
p
# Add mean line
p+ geom_vline(aes(xintercept=mean(kkardashtemp)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$kkardashtemp),' sd = ',sd(my1000$kkardashtemp)))
```

```{r}
numb=2
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k2 = x.avg

p <- ggplot(my1000, aes(x=k2)) + 
  geom_density() 
p

# Add mean line
  geom_vline(aes(xintercept=mean(k2)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$k2),' sd = ',sd(my1000$k2)))

```
## We expect the sample mean to be close to population and the standev to get smaller by the ratio of one to the sample size. In this case 1/sqrt(2)

### There are 3 peaks in the density plot. You pick two people you can get MM,MF.FM,or FF. these are all equally likey so the little peak on left is all the FF's while the little peak on the right is all the MM's so the big one in the middle is both the MF and FM in the same bag so-to-speak.  

```{r}
numb = 4
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k4 = x.avg


p <- ggplot(my1000, aes(x=k4),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k4)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 4") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k4),' sd = ',sd(my1000$k4)))

```

### In this case the stdev was cut in half because the sample size was four. This is what the central limit theorem says. There are also 5 peaks. They go from FFFF,to FFFM, to FFMM to FMMM and finally MMMM.

# Now finish by adding blocks with numb being 9, then 16, 25, and 36. be sure to mention how the standard deviation progresses as the sample size changes,

```{r}
numb=9
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k9 = x.avg

p <- ggplot(my1000, aes(x=k9)) + 
  geom_density() 
p

# Add mean line
  geom_vline(aes(xintercept=mean(k9)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$k9),' sd = ',sd(my1000$k9)))

```

I analyzed our sample size of 9. According to the Central Limits Theorem, the graph shows that the mean gets closer to 50 if rounded up, while standard deviation is decreasing. This is because it's expected to decrease when the sample standard deviation is 42.0198675541614. When increasing the sample size, we divide the sample standard deviation by square root of 9. This results in 14.0066225 which is similar to the sample size of 14.

```{r}
numb=16
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k16 = x.avg

p <- ggplot(my1000, aes(x=k16)) + 
  geom_density() 
p

# Add mean line
  geom_vline(aes(xintercept=mean(k16)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$k16),' sd = ',sd(my1000$k16)))

```

This graph has a sample size of 16. According to the CLT, standard deviation is expected to decrease due to the sample standard deviation of 42.0198675541614. Dividing this number gives us 10.5049669, which is closer to the result I originally found. Because of this, the graph is becoming symmetrical.

```{r}
numb=25
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k25 = x.avg

p <- ggplot(my1000, aes(x=k25)) + 
  geom_density() 
p

# Add mean line
  geom_vline(aes(xintercept=mean(k25)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$k25),' sd = ',sd(my1000$k25)))

```

This graph has a sample size of 25. The CLT tells us if the mean is rounded up, the standard deviation will go down. The standard deviation is 42.0198675541614. Dividing this by 25 gives us 8.40397351, which is closer to the original result. This rounds down to 8.4, which gives us a symmetrical graph.
